Vegetation regrowth/encroachment (gjengroing)

### 2023-08-31 DRAFT_functional_plant_indicators_seminat.Rmd
finalizing fpi markdown for seminat

# making the plot, ANO
ggplot(res.seminat.ANO, aes(x=factor(hovedtype_rute), y=scaled_value, fill=fp_ind)) + 
  geom_hline(yintercept=0.6, linetype="dashed") + 
  geom_violin(color=NA) +
#  geom_boxplot(width=0.2, color="grey") +
  geom_point(size=1, shape=16, color="black") +
  facet_wrap(~factor(fp_ind,levels=c("Light1","Moist1","pH1","Nitrogen1","Phosphorus1","Grazing_mowing1","Soil_disturbance1",
                                     "Light2","Moist2","pH2","Nitrogen2","Phosphorus2","Grazing_mowing2","Soil_disturbance2")), ncol = 7) + 
  xlab("Main ecosystem type") + 
  ylab("Scaled indicator value (ANO data)")

# making the plot, ASO
res.seminat.ASO$NiN_grunntype2 <- substring(res.seminat.ASO$NiN_grunntype,5)
ggplot(res.seminat.ASO, aes(x=factor(NiN_grunntype2), y=scaled_value, fill=fp_ind)) + 
  geom_hline(yintercept=0.6, linetype="dashed") + 
  geom_violin(color = NA) +
  #  geom_boxplot(width=0.2, color="grey") +
  geom_point(size=1, shape=16, color="black") +
  facet_wrap(~factor(fp_ind,levels=c("Light1","Moist1","pH1","Nitrogen1","Phosphorus1","Grazing_mowing1","Soil_disturbance1",
                                     "Light2","Moist2","pH2","Nitrogen2","Phosphorus2","Grazing_mowing2","Soil_disturbance2")), ncol = 7) + 
  xlab("T32 (semi-natural meadow) basic ecosystem type") + 
  ylab("Scaled indicator value (ASO data)")

>>>>

# making the plot, ANO Light, Moist & pH
ggplot(data=subset(res.seminat.ANO,!is.na(scaled_value) & fp_ind %in% c("Light1","Moist1","pH1",
                                                                        "Light2","Moist2","pH2"))
       , aes(x=factor(hovedtype_rute), y=scaled_value, fill=fp_ind)) + 
  geom_hline(yintercept=0.6, linetype="dashed") + 
  geom_violin(color=NA) +
  #  geom_boxplot(width=0.2, color="grey") +
  geom_point(size=1, shape=16, color="black") +
  facet_wrap(~factor(fp_ind,levels=c("Light1","Moist1","pH1",
                                     "Light2","Moist2","pH2")), ncol = 3) + 
  xlab("Main ecosystem type") + 
  ylab("Scaled indicator value (ANO data)") +
  theme(legend.position="none")

# making the plot, ANO Nitrogen, Phosphorus, Grazing_mowing, Soil_disturbance
ggplot(data=subset(res.seminat.ANO,!is.na(scaled_value) & fp_ind %in% c("Nitrogen1","Phosphorus1","Grazing_mowing1","Soil_disturbance1",
                                                                        "Nitrogen2","Phosphorus2","Grazing_mowing2","Soil_disturbance2"))
       , aes(x=factor(hovedtype_rute), y=scaled_value, fill=fp_ind)) + 
  geom_hline(yintercept=0.6, linetype="dashed") + 
  geom_violin(color=NA) +
  #  geom_boxplot(width=0.2, color="grey") +
  geom_point(size=1, shape=16, color="black") +
  facet_wrap(~factor(fp_ind,levels=c("Nitrogen1","Phosphorus1","Grazing_mowing1","Soil_disturbance1",
                                     "Nitrogen2","Phosphorus2","Grazing_mowing2","Soil_disturbance2")), ncol = 4) + 
  xlab("Main ecosystem type") + 
  ylab("Scaled indicator value (ANO data)") +
  theme(legend.position="none")

# making the plot, ASO Light, Moist, pH1
ggplot(data=subset(res.seminat.ASO,!is.na(scaled_value) & fp_ind %in% c("Light1","Moist1","pH1",
                                                                        "Light2","Moist2","pH2")),
       aes(x=factor(NiN_grunntype2), y=scaled_value, fill=fp_ind)) + 
  geom_hline(yintercept=0.6, linetype="dashed") + 
  geom_violin(color = NA) +
  #  geom_boxplot(width=0.2, color="grey") +
  geom_point(size=1, shape=16, color="black") +
  facet_wrap(~factor(fp_ind,levels=c("Light1","Moist1","pH1",
                                     "Light2","Moist2","pH2")), ncol = 3) + 
  xlab("T32 (semi-natural meadow) basic ecosystem type") + 
  ylab("Scaled indicator value (ASO data)") +
  theme(legend.position="none") +
  theme(axis.text.x = element_text(angle = -45, vjust = 0.5, hjust=0.2))

# making the plot, ASO Nitrogen, Phosphorus, Grazing_mowing, Soil_disturbance
ggplot(data=subset(res.seminat.ASO,!is.na(scaled_value) & fp_ind %in% c("Nitrogen1","Phosphorus1","Grazing_mowing1","Soil_disturbance1",
                                                                        "Nitrogen2","Phosphorus2","Grazing_mowing2","Soil_disturbance2")),
       aes(x=factor(NiN_grunntype2), y=scaled_value, fill=fp_ind)) + 
  geom_hline(yintercept=0.6, linetype="dashed") + 
  geom_violin(color = NA) +
  #  geom_boxplot(width=0.2, color="grey") +
  geom_point(size=1, shape=16, color="black") +
  facet_wrap(~factor(fp_ind,levels=c("Nitrogen1","Phosphorus1","Grazing_mowing1","Soil_disturbance1",
                                     "Nitrogen2","Phosphorus2","Grazing_mowing2","Soil_disturbance2")), ncol = 4) + 
  xlab("T32 (semi-natural meadow) basic ecosystem type") + 
  ylab("Scaled indicator value (ASO data)")  +
  theme(legend.position="none") +
  theme(axis.text.x = element_text(angle = -45, vjust = 0.5, hjust=0.2))
